Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-06-16 cmsb22.tex
Updated Table 1
Updated Table 2

\setlength{\tabcolsep}{4pt}
\begin{table}[!htb]
  \caption{\revise{Timing comparisons between PyBoolNet, mpbn and Trappist on the PyBoolNet repository.
    Column \(n\) denotes the number of nodes of each model. Column \(|M|\) denotes the number of minimal trap spaces and for each method is given the computation time in seconds, asking only for the first 1000 trap spaces.
    A number in bold indicates a ratio greater than three compared to the best result. ``NM'' indicates a non-locally-monotonic model.}}
  \centering%
  \label{tab:pyboolnet_repo}
  \begin{tabular}{rlrrrrrrr}
    \toprule
    & model & $n$ & $|M|$ & PyBoolNet & mpbn & Trappist \\ \midrule
    \rownb & arellano\_rootstem & 9 & 4 & 0.05 & 0.01 & \textbf{0.25}\\
    \rownb & calzone\_cellfate & 28 & 27 & 0.03 & \textbf{NM} & 0.03\\
    \rownb & dahlhaus\_neuroplastoma & 23 & 32 & 0.09 & 0.02 & 0.03\\
    \rownb & davidich\_yeast & 10 & 12 & 0.03 & 0.01 & 0.02\\
    \rownb & dinwoodie\_life & 15 & 7 & 0.03 & 0.01 & 0.01\\
    \rownb & dinwoodie\_stomatal & 13 & 1 & 0.03 & 0.01 & 0.01\\
    \rownb & faure\_cellcycle & 10 & 2 & 0.04 & 0.01 & 0.01\\
    \rownb & grieco\_mapk & 53 & 18 & 0.04 & 0.04 & 0.03\\
    \rownb & irons\_yeast & 18 & 1 & 0.04 & 0.01 & 0.02\\
    \rownb & jaoude\_thdiff & 103 & >1000 & \textbf{1.43} & \textbf{1.20} & 0.06\\
    \rownb & klamt\_tcr & 40 & 8 & 0.04 & 0.02 & 0.01\\
    \rownb & krumsiek\_myeloid & 11 & 6 & 0.03 & 0.01 & 0.01\\
    \rownb & multivalued & 13 & 4 & 0.02 & 0.01 & 0.01\\
    \rownb & n12c5 & 11 & 5 & \textbf{35.21} & 0.02 & 0.02\\
    \rownb & n3s1c1a & 2 & 2 & 0.03 & 0.01 & 0.01\\
    \rownb & n3s1c1b & 2 & 2 & 0.03 & 0.01 & 0.01\\
    \rownb & n5s3 & 4 & 3 & 0.03 & \textbf{NM} & 0.01\\
    \rownb & n6s1c2 & 5 & 3 & 0.04 & 0.01 & 0.01\\
    \rownb & n7s3 & 6 & 3 & 0.03 & 0.01 & 0.01\\
    \rownb & raf & 3 & 2 & 0.03 & 0.01 & 0.01\\
    \rownb & randomnet\_n15k3 & 15 & 3 & 0.04 & \textbf{NM} & 0.01\\
    \rownb & randomnet\_n7k3 & 7 & 10 & 0.03 & \textbf{NM} & 0.01\\
    \rownb & remy\_tumorigenesis & 34 & 25 & \textbf{2.41} & 0.03 & 0.02\\
    \rownb & saadatpour\_guardcell & 13 & 1 & 0.05 & 0.01 & 0.01\\
    \rownb & selvaggio\_emt & 56 & >1000 & \textbf{1.75} & \textbf{0.64} & 0.04\\
    \rownb & tournier\_apoptosis & 12 & 3 & 0.06 & 0.01 & 0.01\\
    \rownb & xiao\_wnt5a & 7 & 4 & 0.04 & 0.01 & 0.01\\
    \rownb & zhang\_tlgl & 60 & 156 & 0.33 & \textbf{NM} & 0.04\\
    \rownb & zhang\_tlgl\_v2 & 60 & 258 & 0.12 & 0.18 & 0.03\\
    \bottomrule
  \end{tabular}
\end{table}
\setcounter{rownumber}{0}

@@

    \rownb & inflammatory-bowel~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 47 & 0 & 1 & DNF & NM & 0.82 & 0.69\\

@@

    \rownb & butanol-production~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 66 & 13 & 8192 & 0.71 & NM & 0.02 & 0.02\\
    \rownb & colon-cancer~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 70 & 1 & 10 & 0.20 & NM & 0.01 & 0.01\\

@@

    \rownb & Corral-ThIL-17-diff~\cite{corral2021interplay} & 92 & 16 & >1000 & DNF & NM & 0.06 & DNF\\
    \rownb & Korkut-2015~\cite{lee2019signal} & 99 & 12 & 18556 & DNF & 1.50 & 0.07 & 0.08\\ \midrule
    \rownb & adhesion-cip-migration~\cite{guberman2020boolean} & 121 & 4 & 78 & 36.80 & 0.35 & 0.08 & 0.09\\

@@

    \rownb & influenza-replication~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 131 & 11 & 10128 & 46.67 & NM & 0.03 & 0.02\\
    \rownb & prostate-cancer~\cite{Montagud2021} & 133 & 11 & 2760 & DNF & NM & 0.05 & 0.04\\
    \rownb & HIV-1~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 138 & 14 & 39424 & DNF & NM & 0.03 & 0.06\\
    \rownb & fibroblasts~\cite{helikar2008emergent} & 139 & 9 & >1000 & DNF & NM & 0.06 & DNF\\

@@

    \rownb & kynurenine-pathway~\cite{ostaszewski2021covid19} & 150 & 72 & >1000 & DNF & NM & 0.11 & DNF\\
    \rownb & virus-replication-cycle~\cite{ostaszewski2021covid19} & 154 & 25 & >1000 & DNF & NM & 0.19 & DNF\\
    \rownb & immune-system~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 164 & 13 & >1000 & DNF & NM & 0.11 & DNF\\
    \rownb & RA-apoptosis~\cite{aghamiri2020automated} & 180 & 59 & >1000 & DNF & NM & 0.05 & DNF\\
    \rownb & MAPK~\cite{aghamiri2020automated} & 181 & 37 & >1000 & 87.13 & NM & 0.04 & DNF\\

@@

    \rownb & CHO-2016~\cite{lee2019signal} & 200 & 13 & 13312 & DNF & 3.19 & 0.06 & 0.08\\

@@

    \rownb & ErbB-receptor-signaling~\cite{helikar2013comprehensive} & 247 & 22 & >1000 & DNF & NM & 0.23 & DNF\\
    \rownb & macrophage-activation~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 321 & 19 & >1000 & 16.43 & NM & 0.04 & DNF\\
    \rownb & cholocystokinin~\cite{aghamiri2020automated} & 383 & 74 & >1000 & 1.42 & NM & 0.14 & DNF\\
    \rownb & Alzheimer~\cite{aghamiri2020automated} & 762 & 237 & >1000 & DNF & NM & 0.27 & DNF\\ \midrule
    \rownb & KEGG-network~\cite{DBLP:journals/bmcsb/Kwon16} & 1659 & 521 & >1000 & DNF & 23.44 & 3.60 & DNF\\
    \rownb & human-network~\cite{kim2011reduction} & 1953 & 669 & >1000 & DNF & 25.63 & 5.77 & DNF\\
    \rownb & SN-5~\cite{kim2013rmod} & 2746 & 829 & >1000 & DNF & 33.57 & DNF & DNF\\

>>>>

\setlength{\tabcolsep}{4pt}
\begin{table}[!htb]
  \caption{\revise{Timing comparisons between PyBoolNet, mpbn and Trappist on the PyBoolNet repository.
    Column \(n\) denotes the number of nodes of each model. Column \(|M|\) denotes the number of minimal trap spaces and for each method is given the computation time in seconds, asking only for the first 1000 trap spaces.
    A number in bold indicates a ratio greater than three compared to the best result. ``NM'' indicates a non-locally-monotonic model.}}
  \centering%
  \label{tab:pyboolnet_repo}
  \begin{tabular}{rlrrrrrrr}
    \toprule
    & model & $n$ & $|M|$ & PyBoolNet & mpbn & Trappist \\ \midrule
    \rownb & arellano\_rootstem & 9 & 4 & 0.05 & 0.01 & \textbf{0.20}\\
    \rownb & calzone\_cellfate & 28 & 27 & 0.03 & \textbf{NM} & 0.03\\
    \rownb & dahlhaus\_neuroplastoma & 23 & 32 & 0.05 & 0.02 & 0.03\\
    \rownb & davidich\_yeast & 10 & 12 & 0.04 & 0.01 & 0.02\\
    \rownb & dinwoodie\_life & 15 & 7 & 0.03 & 0.01 & 0.01\\
    \rownb & dinwoodie\_stomatal & 13 & 1 & 0.03 & 0.01 & 0.01\\
    \rownb & faure\_cellcycle & 10 & 2 & 0.04 & 0.01 & 0.02\\
    \rownb & grieco\_mapk & 53 & 18 & 0.04 & 0.02 & 0.02\\
    \rownb & irons\_yeast & 18 & 1 & 0.05 & 0.01 & 0.02\\
    \rownb & jaoude\_thdiff & 103 & >1000 & \textbf{1.44} & \textbf{0.90} & 0.09\\
    \rownb & klamt\_tcr & 40 & 8 & 0.04 & 0.01 & 0.03\\
    \rownb & krumsiek\_myeloid & 11 & 6 & 0.03 & 0.01 & 0.01\\
    \rownb & multivalued & 13 & 4 & 0.03 & 0.01 & 0.01\\
    \rownb & n12c5 & 11 & 5 & \textbf{35.16} & 0.01 & 0.02\\
    \rownb & n3s1c1a & 2 & 2 & 0.02 & 0.01 & 0.01\\
    \rownb & n3s1c1b & 2 & 2 & 0.02 & 0.01 & 0.01\\
    \rownb & n5s3 & 4 & 3 & 0.03 & \textbf{NM} & 0.01\\
    \rownb & n6s1c2 & 5 & 3 & 0.03 & 0.01 & 0.01\\
    \rownb & n7s3 & 6 & 3 & 0.02 & 0.01 & 0.01\\
    \rownb & raf & 3 & 2 & 0.02 & 0.01 & 0.01\\
    \rownb & randomnet\_n15k3 & 15 & 3 & 0.03 & \textbf{NM} & 0.01\\
    \rownb & randomnet\_n7k3 & 7 & 10 & 0.03 & \textbf{NM} & 0.01\\
    \rownb & remy\_tumorigenesis & 34 & 25 & \textbf{2.14} & 0.02 & 0.02\\
    \rownb & saadatpour\_guardcell & 13 & 1 & 0.03 & 0.01 & 0.01\\
    \rownb & selvaggio\_emt & 56 & >1000 & \textbf{1.02} & \textbf{0.52} & 0.09\\
    \rownb & tournier\_apoptosis & 12 & 3 & 0.04 & 0.01 & 0.01\\
    \rownb & xiao\_wnt5a & 7 & 4 & 0.03 & 0.01 & 0.01\\
    \rownb & zhang\_tlgl & 60 & 156 & 0.22 & \textbf{NM} & 0.05\\
    \rownb & zhang\_tlgl\_v2 & 60 & 258 & 0.09 & 0.15 & 0.02\\
    \bottomrule
  \end{tabular}
\end{table}
\setcounter{rownumber}{0}

@@

    \rownb & inflammatory-bowel~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 47 & 0 & 1 & DNF & NM & 1.26 & 0.69\\

@@

    \rownb & butanol-production~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 66 & 13 & 8192 & 0.71 & NM & 0.01 & 0.02\\
    \rownb & colon-cancer~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 70 & 1 & 10 & 0.20 & NM & 0.02 & 0.01\\

@@

    \rownb & Corral-ThIL-17-diff~\cite{corral2021interplay} & 92 & 16 & >1000 & DNF & NM & 0.03 & DNF\\
    \rownb & Korkut-2015~\cite{lee2019signal} & 99 & 12 & 18556 & DNF & 1.04 & 0.06 & 0.08\\ \midrule
    \rownb & adhesion-cip-migration~\cite{guberman2020boolean} & 121 & 4 & 78 & 36.80 & 0.35 & 0.27 & 0.09\\

@@

    \rownb & influenza-replication~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 131 & 11 & 10128 & 46.67 & NM & 0.02 & 0.02\\
    \rownb & prostate-cancer~\cite{Montagud2021} & 133 & 11 & 2760 & DNF & NM & 0.16 & 0.04\\
    \rownb & HIV-1~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 138 & 14 & 39424 & DNF & NM & 0.06 & 0.06\\
    \rownb & fibroblasts~\cite{helikar2008emergent} & 139 & 9 & >1000 & DNF & NM & 0.08 & DNF\\

@@

    \rownb & kynurenine-pathway~\cite{ostaszewski2021covid19} & 150 & 72 & >1000 & DNF & NM & 0.19 & DNF\\
    \rownb & virus-replication-cycle~\cite{ostaszewski2021covid19} & 154 & 25 & >1000 & DNF & NM & 0.03 & DNF\\
    \rownb & immune-system~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 164 & 13 & >1000 & DNF & NM & 0.08 & DNF\\
    \rownb & RA-apoptosis~\cite{aghamiri2020automated} & 180 & 59 & >1000 & DNF & NM & 0.02 & DNF\\
    \rownb & MAPK~\cite{aghamiri2020automated} & 181 & 37 & >1000 & 87.13 & NM & 0.03 & DNF\\

@@

    \rownb & CHO-2016~\cite{lee2019signal} & 200 & 13 & 13312 & DNF & 2.45 & 0.07 & 0.08\\

@@

    \rownb & ErbB-receptor-signaling~\cite{helikar2013comprehensive} & 247 & 22 & >1000 & DNF & NM & 0.24 & DNF\\
    \rownb & macrophage-activation~\cite{DBLP:journals/bmcsb/HelikarKMBRMWSLR12} & 321 & 19 & >1000 & 16.43 & NM & 0.05 & DNF\\
    \rownb & cholocystokinin~\cite{aghamiri2020automated} & 383 & 74 & >1000 & 1.42 & NM & 0.08 & DNF\\
    \rownb & Alzheimer~\cite{aghamiri2020automated} & 762 & 237 & >1000 & DNF & NM & 0.29 & DNF\\ \midrule
    \rownb & KEGG-network~\cite{DBLP:journals/bmcsb/Kwon16} & 1659 & 521 & >1000 & DNF & 20.76 & 3.40 & DNF\\
    \rownb & human-network~\cite{kim2011reduction} & 1953 & 669 & >1000 & DNF & 23.62 & 5.93 & DNF\\
    \rownb & SN-5~\cite{kim2013rmod} & 2746 & 829 & >1000 & DNF & 28.94 & DNF & DNF\\
